### 2020-02-22 README.Rmd
spelling
Have store() use seperate registry for local content
This seperate registry follows the BagIt format, which may be a mistake.  Perhaps it would be better to follow the same registry format as before, but just use separate files (and relative file paths)?

The motivation for BagIt here is that it's a well-defined standard that matches the pattern of publishing a store pretty closely.  (Of course, since content path is just derived from the sha-256 hash, the manifest is pretty redundant.  but BagIt does have a well defined convention for the 'root' of a local/relative path, which is why

Consider a classic dataset, in this case, the Vostok ice core data analyzed by [Barnola et al (1987)](https://doi.org/10.1038/20859 "Barnola, J., Raynaud, D., Korotkevich, Y. et al. Vostok ice core provides 160,000-year record of atmospheric CO2. Nature 329, 408–414 (1987)").  For convenience, a copy of the data is included in this package.  Let's take a peak at the data now:

@@

```{r}
# Oh no, the official version is 503 errors.  Lets use this backup
co2_url <- "https://github.com/espm-157/climate-template/releases/download/data/vostok.icecore.co2"
register(co2_url)
```

>>>>

Consider a classic dataset, in this case, the Vostok ice core data analyzed by [Barnola et al (1987)](https://doi.org/10.1038/329408a0 "Barnola, J., Raynaud, D., Korotkevich, Y. et al. Vostok ice core provides 160,000-year record of atmospheric CO2. Nature 329, 408–414 (1987)").  For convenience, a copy of the data is included in this package.  Let's take a peak at the data now:

@@

```{r}
# Oh no, the official version is 503 errors.  Lets use this backup
co2_url <- "https://zenodo.org/record/3678928/files/vostok.icecore.co2"
register(co2_url)
```
